On Solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization by greedy methods and their hybridizations

### 2020-10-04 doc/paper.tex
update
dodao motivaciju

    \section{Introduction}\label{sec:introduction}
     \emph{The Orthogonal Art Gallery Problem} (OAGP) is one of many variants of Art Gallery Problem (AGP). AGP asks for a set of points $G$ of minimal cardinality on some polygon $P$ such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$.  Set $G$ is called guard set of $P$ and the points from $G$ as guards. The orthogonal AGP consider on arbitrary polygon but whose angles are $90^{\circ}$ and $270^{\circ}$. This problem was stated by Victor  Klee in 1973.~\cite{o1987art}. The problem is motivated from installing the cameras inside a building (or gallery) such that the whole area of the building is covered. Orthogonality constraint naturally comes out from the orthogonality of the walls in buildings.

     Kahn et al. in ~\cite{kahn1983traditional} formulated and proofed that 	$\lfloor \frac{n}{4} \rfloor$ guards are  sufficient to cover an orthogonal polygon with $n$ vertices.  A variant of the OAGP for which we are interested in this study allows only that guards are positioned at the vertices of polygon $P$. Actually, we are looking for minimum vertex guards needed to cover an orthogonal polygon. This restricted problem is known to be NP- hard in ~\cite{schuchardt1995two,katz2008guarding}.

     By discretization $D(P)$ the set of points of the polygon $P$, the art gallery problem can be reduced to the well-known Min Set Cover Problem.\fxnote{Marko: ovdje fali motivacija zasto radimo diskretizaciju poligona} For each vertex of the polygon $P$, a set of points of visibility is determined. In that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets.

     In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal, is presented for simple polygon with $n$ vertices. Firstly, this algorithm do a partitioning the polygonal region into convex components and construct sets consisting of these convex components. After that, on these constructed sets Johnson’s approximation algorithm ~\cite{johnson1974approximation} for the Minimum set-covering problem (MSC) is applied to get solution.

     An anytime algorithm to compute successively better approximations of the optimum to Minimum Vertex Guard is proposed in ~\cite{tomas2003approximation}.  A major idea of this approach is exploring dominance of visibility regions to first detect pieces that are
more difficult to guard. The same problem is solved   in ~\cite{tomas2006visibility} by applying successive approximations from  ~\cite{tomas2003approximation}.

Tozoni et a. ~\cite{tozoni2013practical,tozoni2016algorithm}  presented an exact Integer linear programming  (ILP)-based  algorithm, which iteratively generates upper and lower bounds through the resolution of discretized space of the AGP.

More detailed overview of the results on art gallery problems is out the scope of this paper and can be found in a survey paper  ~\cite{ghosh2010approximation2}.

    Couto et al. presented an exact and efficient algorithm for the Orthogonal Art Gallery Problem in ~\cite{couto2007exact}. The algorithm is divided into two phases. In the preprocessing phase an initial discretization is constructed and the Integer Programming model for solving MSC is applied.  In the solution phase, the discretized instance is iteratively refined and solved, until the solution becomes viable. \fxnote{Marko: ja bih ovdje samo rekao:  Couto et al. an efficient exact algorithm  for OAGP  based on preprocessing and refinement phases of the the discretized instance. }
\subsection{Problem definition}

\subsection{Main contributions}
The main contributions of this paper are:
\begin{itemize}
\item We developed a novel greedy approach which is based on balancing the trade off between the total sum of guards' costs and the total number of not yet covered points from the discretization.
\item We developed a specially designed shaking procedure, which perturbs the current partial solution in such a way that some vertices are replaced with others based on a distance measure.\fxnote{TODO: popraviti}
\item Both an existing and the novel greedy algorithms are hybridized with the proposed shaking procedure and with the ILP
\item We considered different types of weights for our benchmarks, based on a... \fxnote{TODO}
\end{itemize}

     \fxnote{TODO: work on literature approaches}
     %\section{Preliminaries}

@@

     \section{Exact methods}\fxnote{TODO: Marko}
     \subsection{Integer linear programming method}
     Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.  Our task is to cover all points from $D(P)$ by some vertices from $P$ such that the sum of their weights is minimized. 
     The problem is related to the known Minimal Weighted Set-Cover (MWSC) problem. 
     Family $\mathcal{F}\subseteq D(P)$ of nonempty sets consists of sets
      $S_i \in \mathcal{F}$ which include point $p \in D(P)$ that is visible from guard $v_i\in V$, that is $pv_i \subset P$.  Note that set $S_i$ includes a point $p_i$ which can also included by some other guard $v_j\in V$, $i \neq j$. In this was, the task is equivalent of  finding a minimum cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
     $$ \bigcup_{C \in \mathcal{C}} C = D(P).$$ The IP  model for the Weighted Set Cover problem is well-known in the literature, and is here adapted for our task as follows:
     \begin{align}
        &\sum_{i=1}^n w_ix_i \longrightarrow \min \\
        &\mbox{s.t.} \\
        &\sum_{j\in V} a_{ij}x_j \geq 1\ (\forall p_i\in D(P)) \label{eq:const-3}\\
        & x_j \in \{0,1\}, j \in V,
     \end{align}
     where
     $a_{ij} = \begin{cases}
          1, p_i \in V(j), \\
          0, \mbox{otherwise}
     \end{cases}$
     and $x_i = \begin{cases}
     	 1, \mbox{ if } \mbox{ the point } p_i \in \mathcal{C},\\
     	 0, \mbox{otherwise},
     \end{cases}$ \\
      where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
     Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
     Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.

    Introducing the prices into the basic problem can be augmented by the fact that prices of cameras are usually not equal and they are related to their quality (respecting the range of spectrum of view) or due to the fact that installing cameras at some specific corners is much harder than to some other areas.

      In order to solve this model, we apply a general purpose solver \textsc{Cplex}.
       \subsection{Constraint programming method} An equivalent CP model was implemented and tested by CP Optimizer. In this case,  Constraint~(\ref{eq:const-3}) is transformed into 
       \begin{equation}
           \bigvee_{ j \in V } (a_{ij} \wedge x_j) = 1, 
       \end{equation}
      whereas the other constraints and the objective function are the same like in the above MIP model. 
     \section{Algorithmic Approaches for WOAGP}
     \subsection{Greedy approaches for solving WOAGP}
      Since the WOAGP can be seen as the Weighted Set Cover problem (WSCP) and since the best known heuristics to solve WSCP is an enhanced greedy heuristic, our idea is to transform a WOAGP instance into a WSC problem instance and then
          apply greedy algorithms to solve WOAGP. These algorithms produce a solution of reasonable quality within a short interval of time. Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. Among all candidates (solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value until the solution is complete (i.e., cover all  points from $D(P)$).
          A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}

@@

    %  \subsection{Greedy Criterion based on Price-per-Unit}
      Concerning the literature for WSC problem~\ref{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
     \begin{align}
     g(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
     \end{align}
     where $f(s^p) = |\bigcup_{s \in s^p} s |$.
     This heuristic is also a approximation algorithm which ensures $O(\log(n))$ approximation factor.

@@

            In the Equation  (\ref{eq:greedyfun4}) the second term is also normalized and the trade off between two terms is more balanced.
            In this case, the algorithm does not  ultimately prefer any of criteria\fxnote{TODO...}
            \begin{itemize}

\item start Greedy with empty solution
			\item in each iteration add such a guard to $s^{ps}$ for which the obj value is minimal
			\item end when $incorrect_{total}$ becomes 0
          \end{itemize}
      Ties occurred in the search are broken by using  price-per-unit heuristic which i stated as follows.
       For each not yet considered guards $p_i$, we assign the region which is visible from $p_i$ by $S(p_j)$. As the next candidate to extend $s^P$, we choose a guard $p^*$ which covers set $V(j)$ by smallest price per unit, among the other candidate to extend $s^P$. More precisely, greedy criterion $g$ is given as:
      \begin{align}
      g(s^p, p_i) = \frac{w_{p_i}}{S_{p_i}},
      \end{align}
      and $p^*$ that minimizes $g(s^p, p^*)$ value is chosen as an extension of the current partial solution.
      In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics.
     \subsubsection{Partial calculation of objective function}

@@

     \section{Computational Results}
       We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
       \begin{itemize}
       	  \item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
       	 \item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
       	 \begin{equation}
       	   w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n. 
       	 \end{equation}
       \end{itemize}
     \section{Conclusions and Future Work}

>>>>

    \section{Introduction}\label{sec:introduction}

    For a given polygon $P$, Art Gallery Problem (AGP) asks for a set of points $G$ of minimal cardinality,  such that for each point $y \in P$ there is $x \in G$ such that $xy \subset P$. We say that the point $y$ is covered by the point $x$, or $y$ is visible from $x$. Set $G$ is called guard set of $P$ and the points from $G$ as guards. In \emph{The Orthogonal Art Gallery Problem} (OAGP) edges of the polygon are only horizontal and vertical, i.e. angles between adjacent edges are  $90^{\circ}$ or $270^{\circ}$. The original AGP was stated by Victor  Klee in 1973.~\cite{o1987art}.  The problem can be motivated from installing the cameras inside a building (or gallery) such that the whole area of the building is covered. Orthogonality constraint naturally comes out from the orthogonality of the walls in buildings. Kahn et al. in ~\cite{kahn1983traditional} formulated and proofed that 	$\lfloor \frac{n}{4} \rfloor$ guards are  sufficient to cover an orthogonal polygon with $n$ vertices.      In this study, we are interested in the variant of the OAGP which allows only that guards are positioned at the vertices of polygon $P$. This restricted problem is known to be NP- hard in ~\cite{schuchardt1995two,katz2008guarding}.  In real situations (like installing the cameras in a building) , it is justified to assume that the prices of cameras are not equal and may depends on several factors, like the quality of a camera   (respecting the range of spectrum of view)  or installation price at some specific parts of the building (like corners or tight places).  In Weighted Orthogonal Art Gallery Problem (WOAGP), which we finally consider in this paper, the task is to place guards on some vertices of the orthogonal polygon which cover all points from $P$, such that the total sum of prices assigned to all chosen vertices is minimal.

     It is well known that AGP can be reduced to the Minimum Set Cover Problem (MSCP) by a discretization of the set of all points of the polygon $P$. The appropriate discretization should be performed in such a way that if each point from the discretized set $D(P)$ is covered, then the whole polygon $P$ is covered. After the discretization is made, for each vertex of the polygon $P$, a set of visible points from $D(P)$ is determined. In that way, the problem of determining the minimum number of guards covering the entire polygon is reduced to determining the minimum number of subsets of points, such that each point from $D(P)$ is included in at least one of the chosen subsets, which is MSCP. Analogously, WOAGP can be reduced to the Weighted Minimum Set Cover Problem (WMSCP).

     Couto et al. presented an exact and efficient exact algorithm for the OAGP based on preprocessing and refinement phases of the the discretized instance. in ~\cite{couto2007exact}. In ~\cite{ghosh2010approximation} an approximate solution of the minimum vertex guard problem, which can be computed in $O(n^4)$ time and the size of the solution is at most $O(\log n)$ times the optimal. After that, on these constructed sets Johnson’s approximation algorithm ~\cite{johnson1974approximation} for the MSCP is applied. An anytime algorithm to compute successively better approximations of the optimum to Minimum Vertex Guard is proposed in ~\cite{tomas2003approximation}.  A major idea of this approach is exploring dominance of visibility regions to first detect pieces that are
more difficult to guard. The same problem is solved   in ~\cite{tomas2006visibility} by applying successive approximations from  ~\cite{tomas2003approximation}.
Tozoni et a. ~\cite{tozoni2013practical,tozoni2016algorithm}  presented an exact Integer linear programming  (ILP)-based  algorithm, which iteratively generates upper and lower bounds through the resolution of discretized space of the AGP. Although many variants AGP are present in literature, WOAGP has not been so intensively studied, which motivated us to consider this problem.
Analysis of many greedy-like heuristic for the WMSCP was presented in \cite{vasko2016best}.
More detailed overview of the extensive literature regarding SCP and AGP is out of the scope of this paper and for further reading we suggest review papers ~\cite{caprara2000algorithms,ren2010new,ghosh2010approximation2}.

\subsection{Problem definition}
\fxnote{TODO: Ovo mozda sad i ne treba?}

\subsection{Main contributions}
The main contributions of this paper are:
\begin{itemize}
\item We developed a novel greedy approach which is based on balancing the trade off between the total sum of guards' costs and the total number of not yet covered points from the discretization.
\item We developed a specially designed shaking procedure, which perturbs the current partial solution in such a way that some vertices are replaced with others, where the replacement is based on measuring  distances between points in the polygon.\fxnote{TODO: popraviti}
\item Both an existing and the novel greedy algorithms are hybridized with the proposed shaking procedure and with the ILP.
\item We considered different types of weights for our benchmarks, based on an approximation of the costs in real situations.
\item In a comprehensive computational experiment, \fxnote{TODO: popraviti} different variants of approximative algorithms we tested and analysed.
\end{itemize}

@@

     \section{Exact methods}\fxnote{TODO: Marko}
     In this section we present the known exact ILP and constraint programming (CP) methods for solving WMSCP, which are used  in the rest of the paper.
     \subsection{Integer linear programming method}
     Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.  Our task is to cover all points from $D(P)$ by some vertices from $P$ such that the sum of their weights is minimized.
     The problem is related to the known Minimal Weighted Set-Cover (MWSC) problem.
     Family $\mathcal{F}\subseteq D(P)$ of nonempty sets consists of sets
      $S_i \in \mathcal{F}$ which include point $p \in D(P)$ that is visible from guard $v_i\in V$, that is $pv_i \subset P$.  Note that set $S_i$ includes a point $p_i$ which can also included by some other guard $v_j\in V$, $i \neq j$. In this was, the task is equivalent of  finding a minimum cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
     $$ \bigcup_{C \in \mathcal{C}} C = D(P).$$ The IP  model for the Weighted Set Cover problem is well-known in the literature, and is here adapted for our task as follows:
     \begin{align}
        &\sum_{i=1}^n w_ix_i \longrightarrow \min \\
        &\mbox{s.t.} \\
        &\sum_{j\in V} a_{ij}x_j \geq 1\ (\forall p_i\in D(P)) \label{eq:const-3}\\
        & x_j \in \{0,1\}, j \in V,
     \end{align}
     where
     $a_{ij} = \begin{cases}
          1, p_i \in V(j), \\
          0, \mbox{otherwise}
     \end{cases}$
     and $x_i = \begin{cases}
     	 1, \mbox{ if } \mbox{ the point } p_i \in \mathcal{C},\\
     	 0, \mbox{otherwise},
     \end{cases}$ \\
      where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
     Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
     Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.

      In order to solve this model, we apply a general purpose solver \textsc{Cplex}.
       \subsection{Constraint programming method} An equivalent CP model was implemented and tested by CP Optimizer. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
       \begin{equation}
           \bigvee_{ j \in V } (a_{ij} \wedge x_j) = 1,
       \end{equation}
      whereas the other constraints and the objective function are the same like in the above MIP model. Note that CP appraoch works in a branch-and-bound manner imploying a constriant propagation and domain filtering~\ref{}.
     \section{Algorithmic Approaches for WOAGP}
     \subsection{Greedy approaches for solving WOAGP}
      Since the WOAGP can be seen as the WMSCP and since the best known heuristics to solve WSCP is an enhanced greedy heuristic \fxnote{Marko, treba nam referenca da je greedy najbolja heuristika}, our idea is to transform a WOAGP instance into a WSC problem instance and then
          apply greedy algorithms to solve WOAGP. These algorithms produce a solution of reasonable quality within a short interval of time. Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. Among all candidates (solution components for expansion, that is not-yet-considered guards, we choose one with the smallest greedy value until the solution is complete (i.e., cover all  points from $D(P)$).
          A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}

@@

    %  \subsection{Greedy Criterion based on Price-per-Unit}
      Concerning the literature for WMSC problem~\ref{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
     \begin{align}
     g(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
     \end{align}
     where $f(s^p) = |\bigcup_{s \in s^p} s |$.
     This heuristic is also a approximation algorithm which ensures $O(\log(n))$ approximation factor.

@@

            In the Equation  (\ref{eq:greedyfun4}) the second term is also normalized and the trade off between two terms is more balanced.
            In this case, the algorithm does not  ultimately prefer any of criteria for choosing next vertex. Instead,  \fxnote{TODO...}

      Ties occurred in the search are broken by using  price-per-unit heuristic which i stated as follows.
       For each not yet considered guards $p_i$, we assign the region which is visible from $p_i$ by $S(p_j)$. As the next candidate to extend $s^P$, we choose a guard $p^*$ which covers set $V(j)$ by smallest price per unit, among the other candidate to extend $s^P$. More precisely, greedy criterion $g$ is given as:
      \begin{align}
      g(s^p, p_i) = \frac{w_{p_i}}{S_{p_i}},
      \end{align}
      and $p^*$ that minimizes $g(s^p, p^*)$ value is chosen as an extension of the current partial solution.
      In our experimental studies, we found out that this heuristic does not perform well on its own, but presents a reasonable tie-breaking mechanism and is able to boost quality of our greedy heuristics.
     \subsubsection{Partial calculation of objective function}

     In order to enable fast calculation of greedy functions described in previous subsections, we introduce several useful structures and auxiliary functions:
      \begin{itemize}
      \item structure \texttt{map<Point,list<Point>> Visibility} -- for each point, we provide the list od guards which see that point; 
      \item structure \texttt{map<Point,int> numberOfGuards} -- for each point we keep the number of Guards in solution which see that point;
       \item structure \texttt{set<Point> CoveredPoints} -- set of points covered by the partial solution;
       \item function \texttt{updateCoveredPointsAdd (vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex \texttt{v}, when \texttt{v} is added to solution;
       \item fucntion \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by \texttt{v}, when \texttt{v} is removed from solution.
      \end{itemize}

@@

     \section{Computational Results}
       We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
       \begin{itemize}
       	  \item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
       	 \item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
       	 \begin{equation}
       	   w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n.
       	 \end{equation}
       \end{itemize}
       \subsection{Results on exact methods}
       ovo za cp i 5min, što je Marko pominjao
     \section{Conclusions and Future Work}
